QPLIB: A Library of Quadratic Programming Instances

### 2018-01-30 methods.tex
Update methods.tex
fixup references and add a question as todo
fix typos, add todo where unsure

@@

To explain this apparent contradiction, we remark that the two statements refer to different computational models: the former is based on the Turing Machine (TM), whereas the latter is based on a computational model that allows operations or real numbers, e.g.~the Real RAM (RRAM) machine \cite{blum}. Due to the potentially infinite nature of exact real arithmetic computations, exact computations on the RRAM necessarily end up being approximate on the TM. Analogously, a complete method may reasonably be called ``exact'' on a RRAM; however, the computers we use in practice are more akin to TMs than RRAMs, and therefore calling \emph{exact} a solver that employs floating point computations is, technically speaking, stretching the meaning of the word. However, because the term is well understood in the computational optimization community, in the following we shall loosen the distinction between complete and exact methods, with either properties intended to mean ``complete'' in the sense of \cite{neumaier}.

Nearly all of the complete solvers in Table \ref{t:solvers} that address $\mathcal{NP}$-hard problems (i.e.~those in \textit{QGQ}$\smallsetminus$\textit{CCC}) are based on Branch-and-Bound (BB) \cite{land_doig}. When the BB algorithm is allowed to branch on coordinate directions corresponding to continuous variables, it is called \emph{spatial} BB (sBB) \cite{dakin,couenne}. BB algorithms are exponential time in the worst case, and their exponential behavior unfortunately often shows up in practice. They can also be used heuristically (forsaking their completeness guarantee) in a number of ways, e.g.~by either terminating them early. The following solvers from Table \ref{t:solvers} implement complete BB algorithms for \textit{QGQ} or some subclasses: 
%
\begin{itemize}
 \item \antigone, \baron, \couenne, \lindo, \scip for \textit{QGQ};
 %
\item \cplex for \textit{QGL} and \textit{CGC};
%
 \item \knitro, \bonmin, \sbb, \xpress, \gurobi, and \mosek for \textit{CGC}.
\end{itemize}
%
We remark that the latter category can be used as incomplete solvers for \textit{QGQ}. We also note that \lgo implements an incomplete BB algorithm for \textit{QCQ} by using bounds obtained from sampling.

>>>>

\textcolor{red}{We refer the interested reader to 
\cite{book:2077007} and 
\cite{Michae-2007}\todo{was it really mean to cite the book review instead of the book here?}\ for further details on the solution methods.}

@@

To explain this apparent contradiction, we remark that the two statements refer to different computational models: the former is based on the Turing Machine (TM), whereas the latter is based on a computational model that allows operations on real numbers, e.g.~the Real RAM (RRAM) machine \cite{blum}. Due to the potentially infinite nature of exact real arithmetic computations, exact computations on the RRAM necessarily end up being approximate on the TM. Analogously, a complete method may reasonably be called ``exact'' on a RRAM; however, the computers we use in practice are more akin to TMs than RRAMs, and therefore calling \emph{exact} a solver that employs floating point computations is, technically speaking, stretching the meaning of the word. However, because the term is well understood in the computational optimization community, in the following we shall loosen the distinction between complete and exact methods, with either properties intended to mean ``complete'' in the sense of \cite{neumaier}.

Nearly all of the complete solvers in Table \ref{t:solvers} that address $\mathcal{NP}$-hard problems (i.e.~those in \textit{QGQ}$\smallsetminus$\textit{CCC}) are based on Branch-and-Bound (BB) \cite{land_doig}. When the BB algorithm is allowed to branch on coordinate directions corresponding to continuous variables, it is called \emph{spatial} BB (sBB) \cite{dakin,couenne}. BB algorithms are\todo{require?}\ exponential time in the worst case, and their exponential behavior unfortunately often shows up in practice. They can also be used heuristically (forsaking their completeness guarantee) in a number of ways, e.g.~by terminating them early. The following solvers from Table \ref{t:solvers} implement complete BB algorithms for \textit{QGQ} or some subclasses: 
%
\begin{itemize}
 \item \antigone, \baron, \couenne, \lindo, \scip for \textit{QGQ};
 %
\item \cplex for \textit{QGL} and \textit{CGC};
%
 \item \knitro, \bonmin, \sbb, \xpress, \gurobi, and \mosek for \textit{CGC}.
\end{itemize}
%
We remark that the latter category can be used as incomplete solvers for \textit{QGQ}. We also note that \lgo implements an incomplete BB algorithm for \textit{QCQ} by using bounds obtained from sampling.
